Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-03 scnn.tex
start with experiment

@@

What do we want to show? The graph CNN is able to discriminate ??? using higher order statistics.

@@

Our data comes from a simulation with software ??? using the following parameters ???. All the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_1.pdf}
\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_2.pdf}
\caption{One sample of each class }
\label{fig:map_sample}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/part_sphere.pdf}
\caption{3 subparts of the sphere with different sizes. Blue: order 1. Green: order 2. Yellow: order 3.}
\label{fig:subpart_sphere}
\end{figure}

>>>>

\todo{Check this unpublished work \cite{khasanova2017graph}}

@@

% Structure of the section
% 1) Present the goal
% 2) Explain briefly the dataset
% 3) Present the setting
% 4) Describe the result
In this section, we demonstrate the usefulness of the spherical neural network
on a discrimination problem. Our implementation is availlable as small python package at \url{https://our.code.link.com}. 
Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}

@@

Our data comes from a simulation with software ??? using the following parameters ???.

As a preprocssing step, we first remove the mean of each sample and apply a
spherical gaussian smoothing kernel with a radius of $1$ arcmin.

We made 30 simulations for each class. Out of the 60 simulations, 20 are kept
for the test set. The training and validation set are created later on.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_1.pdf}
\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_2.pdf}
\caption{One sample of each class.}
\label{fig:map_sample}
\end{figure}

\subsection{Problem formulation}

Leveraging the properties of the HealPix sampling, we can split each simulation
into $12*4^o$ ($o=0,1,2,\dots$) samples that span a smaller part of the sphere.
As shown in Figure~\ref{fig:subpart_sphere}, we used $o=0,1,2$ as the resulting
samples are large enough to suffer from the effet of the spherical geometry. We
decided to only report simulation results for this specific setting as spherical
cosmological data usually does not span the full sphere. However, our code
includes an example using the full sphere.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/part_sphere.pdf}
\caption{3 subparts of the sphere with different sizes. Blue: $o=0$. Green: order $o=1$. Yellow: order $o=2$.}
\label{fig:subpart_sphere}
\end{figure}
